\chapter{Links}

\begin{itemize}
	\item github repository: \url{https://github.com/CowKeyMan/new-particle-formation}
\end{itemize}

\newpage

\chapter{Grading}

\section{Grade for the deliverables: 5/5}

This overall grade was composed of three parts, we will state these individually and give reasons for why we think we deserve the grade that we have given above. We give each part an individual grade which led us to the overall grade stated above.

\begin{itemize}
\item Presentation: 5/5
  \begin{itemize}
    \item The presentation is easy to follow and includes all the important ideas and steps in a short time. Powerpoint presentation was prepared in advance to make the topics presented clear for the reader. Audio was edited to match the slides.
  \end{itemize}
\item Challenge Submission: 4/5
  \begin{itemize}
    \item We did not use the test csv data during model building. Reason for this is that we decided to treat these as completely unseen. In hindsight, it might have been a good idea to use these, but our goal to predict the test data as accurately as possible without using information from it, similar to a real-world scenario where future data is not known and hence models cannot be trained using this future data.
    \item We could have used the test.csv data when fitting our PCA model and the scaler when scaling to mean 0 and unit variance.
  \end{itemize}
\end{itemize}

\begin{itemize}
\item Final Report: 5/5
\begin{itemize}
    \item We trained a variety of classifiers to see how they performed
    \item Our results are justified and thoroughly explained
    \item Multiple techniques from the course were applied and theory from the course was also used during discussion
    \item Extra material beyond the course included:
    \begin{itemize}
      \item using MLP models
      \item using balanced weights for discriminative classifiers
      \item We explain our ideas and process in the report such that it is easy for the reader to follow. Furthermore, visualisations of the data are clear and well-explained.
    \end{itemize}
  \end{itemize}
\end{itemize}

\section{Grade for the group as a whole 5/5}

\begin{itemize}
\item Instructions were always followed closely and deliverables delivered in time and in full
\item Our group had meetings every week mostly at the library, so our project was always in progress and a bit ahead of time.
\item During each meeting we wrote down notes in Notion where everyone can see what was accomplished in the previous week, what was discussed during the meetings, and their tasks for the following week.
    \begin{itemize}
    \item Meetings were always on topic were each member could express their thoughts and ideas freely and debates were encouraged in order to uncover any possible flaws in our methodology.
    \end{itemize}
\item Group meeting were almost like mini lectures where we taught each other things from our background since we each had different backgrounds (math, statistics, computing science)
\end{itemize}
